Light curves of the brightest stars in the Southern sky\\ seen by bRing

### 2023-06-20 src/tex/ms.tex
[showyourwork] overleaf sync

   \date{Received September XX, 2020; accepted XXXX}

@@

@@

We started the data reduction by selecting good data points from the daily and quarterly data. 
\begin{itemize}
    \item First, the long exposures were discarded. Only the short exposures were used, because the long exposures can only be used to observe stars fainter than magnitude 4. This is due to the fact that images taken with long exposure times have a higher chance of being saturated than the short exposures.
    \item Next, we used the astrometry and photometry flags of the daily data. These tell us if the measured flux is too high or too low to be realistic or if no photometry was performed due to the star being too close to the edge of the image, for example. Only the data without any bad flags was used. 
    \item We made sure that the magnitude error for the daily data is always greater than zero and finite, so no incorrect values are encountered.
    \item All data where the Sun is lower than $-18\degr$ was selected. This was added to ensure that the sky background did not get too bright. 
    \item Next, the data points where the cloud error was 3$\sigma$ above the mean cloud error were deleted. The 3$\sigma$ cutoff was estimated by eye. The cloud error tells us how the transmission changes over time; a big change might mean a cloud is in view. These outliers usually indicate that the clouds are variable at that point in time, in which case the data should not be used.
\end{itemize}
After selecting the good data points for the daily and quarterly data, the daily data was calibrated. However, we cannot use the daily data to remove, for example, the clouds, because those values are only available in the quarterly data. A piece of code written by Remko Stuik was applied to transfer the missing information from the quarterly data to the daily data. 
\begin{itemize}
    \item The 5$\sigma$ outliers based on magnitude error were discarded. A big error could mean that the measurement is wrong. 
    \item The 3$\sigma$ outliers for the mean of the clouds were also removed. This results in less background noise.
    \item The final step was to reject the 5$\sigma$ outliers for the mean of the sky background. This rejection also results in less background noise.
\end{itemize}

>>>>

   \date{Received \today; accepted XXXX}

@@

\subsection{Reduction steps in the showyourwork framework}

Raw data is stored in a custom database and retrieved with Python 2.7 scripts on a local computer.

We extract the raw data for each camera and save as a FITS file with the format {\tt <HD number>\_<cameraID>.fits} where {\tt HD number} is the Henry Draper number for the star and {\tt cameraID} is one of the four camera names {\tt AUE,AUW,SAE,SAW}.
%
These raw data are written out using the {\tt save\_raw\_data\_from\_bring\_database.py} script.
%
The resulting 628 data files are 144 Gb in size and are retrievable from the public repository Zenodo at XXXXXX.

@@

We started the data reduction by selecting good data points from the daily and quarterly data. 
\begin{itemize}
    \item First, the long exposures were discarded. Only the short exposures were used, because the long exposures can only be used to observe stars fainter than magnitude 4. This is due to the fact that images taken with long exposure times have a higher chance of being saturated than the short exposures.
    \item Next, we used the astrometry and photometry flags of the daily data. These tell us if the measured flux is too high or too low to be realistic or if no photometry was performed due to the star being too close to the edge of the image, for example. Only the data without any bad flags was used. 
    \item We made sure that the magnitude error for the daily data is always greater than zero and finite, so no incorrect values are encountered. The magnitude values were also ensured to be finite.
    \item All data where the Sun is lower than $-18\degr$ was selected. This was added to ensure that the sky background did not get too bright. 
    \item Next, the data points where the cloud error was 3$\sigma$ above the mean cloud error were deleted. The 3$\sigma$ cutoff was estimated by eye. The cloud error tells us how the transmission changes over time; a big change might mean a cloud is in view. These outliers usually indicate that the clouds are variable at that point in time, in which case the data should not be used.
\end{itemize}
After selecting the good data points for the daily and quarterly data, the daily data was calibrated. However, we cannot use the daily data to remove, for example, the clouds, because those values are only available in the quarterly data. A piece of code written by Remko Stuik was applied to transfer the missing information from the quarterly data to the daily data. 
\begin{itemize}
    \item The 5$\sigma$ outliers based on magnitude error were discarded. A big error could mean that the measurement is wrong. 
    \item The 3$\sigma$ outliers for the mean of the clouds were also removed. This results in less background noise.
    \item The final step was to reject the 5$\sigma$ outliers for the mean of the sky background. This rejection also results in less background noise.
\end{itemize}
